Reply to: 2022-05603 Intentional release of native species undermines ecological stability

### 2022-12-24 rmd/reply_r2.Rmd
Update reply_r2.Rmd

This is a re-submission of a manuscript: "2022­05603 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript. The comments were very helpful in improving our manuscript. When revising the manuscript, we have put a particular emphasis on the following points:

In summary, the improved text/analysis provides clearer evidence that intentional release has destabilizing effects and clarifies its broader relevance to other systems. We appended a point-by-point response below. We hope our manuscript is now suitable for publication in your journal.

@@

\clearpage

@@

@@

> Thank you. This is perhaps because of our unclear writing. At all sites, a combination of electrofishing and cast net was used to capture both benthic and water-column species effectively. We have clarified this in the revised MS (L XXX). In addition, we have added some text to clarify that the sampling has constant sampling effort per unit area. Therefore, our analysis is robust to this issue.

@@

> The secondary analysis at sites with no missing data would be insightful for sure. However, it introduces the issue of sample size. To address reviewer's concern more appropriately, we included "the number of observation years" as a covariate in the regression model. This approach is suitable because it keeps the sample size as original while accounting for potential influences of observation intervals. The results were qualitatively similar.

@@

> Thank you for your careful reading. However, this data point is not identified as an outlier; thus, there is no statistical justification for removing it from analysis. Although the figure was shown in an ordinary scale, the analysis was carried out in a log-scale (see Methods). When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below). Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for outliers in both response (log CV) and predictor variables (effective release). We hope this ameliorates reviewer's concern.

@@

> XXX

@@

> We appreciate this suggestion! We included SD Elevation as an additional covariate in the regression model. The results were qualitatively similar.

@@

> Some of the watersheds (e.g. Shimonaefutoro) do not receive stocking for the purpose of regional population conservation. The rest of variation across watersheds are due largely to logistical reasons (e.g., accessibility). We have briefly mentioned this in the revised MS.

@@

@@

\clearpage

# References

>>>>

This is a revision of a manuscript: "2022­18044 *Intentional release of native species undermines ecological stability.*" Thank you for allowing us to revise our manuscript. We have refined our analysis and text in light of comments from the reviewer 3. We hope the manuscript is suitable for publication in PNAS.

@@

@@

*This revision does a superb job addressing previous concerns that were raised in the review process. These improvements along with the significant content of this research have resulted in an excellent contribution.*

*Before publication, however, the authors need to clarify the text commented on by reviewer #3 (lines 38-39, 44-46, 47-48, 167, and include the Genus for all species.*

> Thank you for your careful reading. We have addressed these concerns. Please see our response to reviewer 3.

*I also recommend a bit more discussion relating to sampling method and its implications for estimated variability (the point raised by reviewer #3).*

> We appreciate your recommendation. We believe our unclear writing has caused a confusion -- please let us clarify.
>
> First, the sampling method in the protected watersheds are consistent across all sites and years, so there is no need to include the sampling method as a control factor in the statistical model (clarified in Methods). Further, the sampling method (a combination of cast net and electrofishing) was carefully chosen to catch both water-column and benthic fish species effectively (clarified and mentioned in Discussion; L. 227 --). Therefore, we believe our data are robust to sampling bias.
>
> Second, we appreciate reviewer's comment on irregular sampling interval. In the revised analysis, we have included the number of observation years as an additional covariate to address reviewer's concern. The results were qualitatively similar. Please see also our response to reviewer 3.
>
> Overall, we confirmed that our results were robust to concerns raised by reviewer 3.

@@

> Thank you. This is perhaps because of our unclear writing. At all sites, a combination of electrofishing and cast net was used to capture both benthic and water-column species effectively. We have clarified this in the revised MS (L 333 --). In addition, we have added some text to clarify that the sampling has constant sampling effort per unit area (see **Supplementary text**). Therefore, our analysis is robust to this issue.

@@

> The secondary analysis at sites with no missing data would be insightful for sure. However, it introduces the issue of sample size. To address reviewer's concern more appropriately, we included "the number of observation years" as a covariate in the regression model. This approach is suitable because it keeps the sample size as original while accounting for potential influences of observation intervals. The results were qualitatively similar, confirming the robustness of our results.

@@

> Thank you for your careful reading. However, this data point is not identified as an outlier; thus, there is no statistical justification for removing it from analysis. Although the figure was shown in an ordinary scale, the analysis was carried out in a log-scale (see Methods). When we applied the Grubb's test to the log-transformed CV, the p-value was 0.176, indicating that our results were not strongly influenced by the highest value of CV (see R codes below). Also, we have confirmed that our results were robust even if we used robust regression with the MM method, which accounts for potential outliers in both response (log CV) and predictor variables (effective release). We hope this ameliorates reviewer's concern.

@@

> Thank you for this comment. We agree with this opinion. However, we believe our analysis has already accounted for this aspect. The main response variable in our analysis (CV) is the aggregate measure of all species present in the community, namely: $CV = \frac{\sqrt{\sum \sigma^2_i + \sum \sum Cov_{ij}}}{\sum \mu_i}$ ($\sigma_i$ is the SD for species $i$). Therefore, the point raised by the reviewer is already accounted in our model, albeit implicitly. Also, we wanted to remind the reviewer that our results indicated that the community SD was not influenced by intentional release. Although we cannot exclude the possible importance of relative community composition, our data suggest that it has a minimal influence on the dynamics (at least in our system).

@@

> We appreciate this suggestion -- We included "SD elevation" as an additional covariate in the regression model. The results were qualitatively similar.

@@

> Some of the watersheds (e.g. Shimonaefutoro) do not receive stocking for the purpose of regional population conservation. The rest of variation across watersheds are due largely to logistical reasons (e.g., accessibility). We have briefly mentioned this in the revised MS (L. 158 --).

@@

> Thank you for the important suggestion. We agree that different types of interactions may be important to understand ecosystem-wide impacts of intentional release. We have clarified this point in the revised manuscript. In the meantime, we believe our research is unique and significant in that we have quantified "long-term" impact at the community level. As the reviewer suggested, there are some discussion on the community-level impact of intentional release (very few though). However, none of them evaluated the long-term impact. We have improved the description about the knowledge gap addressed in this study (L51 --)

@@

> We understood that the reviewer commented on the last paragraph of "theoretical prediction." We have clarified that we are linking our results to reintroduction programs in conservation (paragraph starting at L135).
